\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}

\begin{enumerate}[label={[Pub \arabic*]},leftmargin=3cm]

\item \underline{\textbf{Duy-Cat Can}}, Hoang-Quynh Le, Quang-Thuy Ha, and Nigel Collier. ``A Richer-but-Smarter Shortest Dependency Path with Attentive Augmentation for Relation Extraction.'' In \textit{The 2019 Annual Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies (NAACL-HTL)}, 2019, (In Press).

\item \underline{\textbf{Duy-Cat Can}}, Hoang-Quynh Le, and Quang-Thuy Ha. ``Improving Semantic Relation Extraction System with Compositional Dependency Unit on Enriched Shortest Dependency Path.'' In \textit{The 11th Asian Conference on Intelligent Information and Database Systems (ACIIDS)}, pp. 140-152, Springer, 2019.

\item Trang M. Nguyen, Van-Lien Tran, \underline{\textbf{Duy-Cat Can}}, Quang-Thuy Ha, Ly T. Vu, and Eng-Siong Chng. ``QASA: Advanced Document Retriever for Open-Domain Question Answering by Learning to Rank Question-Aware Self-Attentive Document Representations.'' In \textit{Proceedings of the 3rd International Conference on Machine Learning and Soft Computing}, pp. 221-225. ACM, 2019.

\item \underline{\textbf{Duy-Cat Can}}, Thi-Nga Ho, and Eng-Siong Chng. ``A hybrid deep learning architecture for sentence unit detection.'' In \textit{Proceedings of the 2018 International Conference on Asian Language Processing (IALP)}, pp. 129-132. IEEE, 2018.

\item Thi-Nga Ho, \underline{\textbf{Duy-Cat Can}}, and Eng-Siong Chng. ``An investigation of word embeddings with deep bidirectional lstm for sentence unit detection in automatic speech transcription.'' In \textit{Proceedings of the International Conference on Asian Language Processing (IALP)}, pp. 139-142. IEEE, 2018.

\item Hoang-Quynh Le, \underline{\textbf{Duy-Cat Can}}, Sinh T. Vu, Thanh Hai Dang, Mohammad Taher Pilehvar, and Nigel Collier. ``Large-scale exploration of neural relation classification architectures.'' In \textit{Proceedings of the 2018 Conference on Empirical Methods in Natural Language Processing (EMNLP)}, pp. 2266-2277. 2018.

\end{enumerate}